Appendix

### 2025-03-18 manuscript_rmarkdown/manuscript_appendix.Rmd
Insert critical values for empirical central normality test.

\begin{definition}[Central normality test statistic]
Let $\alpha$ be the significance level for the empirical central normality test.
Let $m$ be the number of elements of $\mathbf{R}_{\text{c}}$

@@

Critical values for the test statistic of the central normality test 
are found in Table \ref{tab:empirical-central-normality-critical-statistic}. 
The null-hypothesis should be rejected at significance level $\alpha$ if 
$\tau_{\alpha, n, \kappa} \geq \tau_{\alpha, n, \kappa, \text{critical}}$.

@@

```{=latex}
\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.70}$ for
central normality at $\kappa = 0.70$, as a function of significance 
level $\alpha$ and number of instances $n$. The values shown must be divided by $100$.}
\label{tab:central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

@@

>>>>

\begin{definition}[Central normality test statistic]
Let $\alpha$ be the significance level for the central normality test.
Let $m$ be the number of elements of $\mathbf{R}_{\text{c}}$

@@

Critical values for the test statistic of the central normality test 
are found in Table \ref{tab:central-normality-critical-statistic}. These are 
determined by repeatedly and randomly sampling data (i.e. $\mathbf{X}$) from
a normal distribution $\mathcal{N}(0,1)$. The null-hypothesis should be rejected
at significance level $\alpha$ if 
$\tau_{\alpha, n, \kappa} \geq \tau_{\alpha, n, \kappa, \text{critical}}$.

The empirical central normality test is a central normality test, in the
definition provided above. However, critical values of the test statistic are
not determined directly from data drawn randomly from $\mathcal{N}(0,1)$.
Rather, after $\mathbf{X}$ is drawn, 10% of the values are randomly replaced by
random outlier values. The resulting distribution is centrally normal, but
not fully normal.

Critical values for the empirical variant of the central normality test are
found in Table \ref{tab:empirical-central-normality-critical-statistic}.

@@

```{=latex}
\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.70}$ for
\textbf{central normality} at $\kappa = 0.70$, as a function of significance 
level $\alpha$ and number of instances $n$. The values shown must be divided by $100$.}
\label{tab:central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

@@

```{=latex}
\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.70}$ for
\textbf{empirical central normality} at $\kappa = 0.70$, as a function of significance 
level $\alpha$ and number of instances $n$. The values shown must be divided by $100$.}
\label{tab:empirical-central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

\midrule
5     & 12.04 & 14.02 & 17.37 & 21.26 & 24.02 & 26.45 & 28.46 & 30.65 & 33.90 \\
10    &  8.75 & 10.23 & 13.82 & 18.53 & 21.58 & 24.31 & 27.01 & 30.82 & 41.82 \\
20    &  6.80 &  7.74 & 10.03 & 13.17 & 15.12 & 16.95 & 18.64 & 20.79 & 25.07 \\
50    &  4.67 &  5.26 &  6.69 &  8.70 &  9.99 & 11.18 & 12.32 & 13.65 & 16.73 \\
100   &  3.38 &  3.79 &  4.83 &  6.21 &  7.13 &  7.97 &  8.72 &  9.72 & 11.78 \\ 
200   &  2.47 &  2.77 &  3.51 &  4.54 &  5.19 &  5.77 &  6.31 &  6.92 &  8.47 \\
500   &  1.65 &  1.86 &  2.38 &  3.06 &  3.47 &  3.85 &  4.19 &  4.62 &  5.58 \\
1000  &  1.27 &  1.44 &  1.84 &  2.35 &  2.65 &  2.90 &  3.15 &  3.43 &  4.08 \\
2000  &  1.06 &  1.20 &  1.53 &  1.91 &  2.13 &  2.32 &  2.48 &  2.68 &  3.08 \\
5000  &  0.95 &  1.07 &  1.30 &  1.56 &  1.69 &  1.81 &  1.91 &  2.04 &  2.30 \\
10000 &  0.96 &  1.05 &  1.23 &  1.41 &  1.50 &  1.58 &  1.65 &  1.75 &  1.92 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```
